---
title: "FGraph"
output:
  html_document: default
  pdf_document: default
---


Clear 
```{r}
rm(list = ls())
```


```{r setup}
#install.packages("remotes")
#Sys.setenv("R_REMOTES_NO_ERRORS_FROM_WARNINGS" = "true")
#remotes::install_github("orange-vertex/rdepthmap")
library(rdepthmap)
library(rgeos)
library(rgdal)
library(maptools)
library(devtools)
library(dplyr)
library(tidyverse)
library(sjmisc)
library(seqHMM) 
library(ggplot2)
library(spatstat)
library(reshape2)
library(networkD3)
library(xml2)
library(rvest)
library(tidyverse)  
library(stringr)   
library(lubridate)
library(data.table)
library(network)
library(sjmisc)
library(igraph)

#install.packages("https://cran.r-project.org/src/contrib/rlang_0.4.11.tar.gz", repos = NULL, type="source")

```


#Read Data
```{r}
data_ = read.csv("Data/Connectivity_6.3.csv") %>% filter (status == "Old") %>% filter (weight == 1) 
data = data_ %>% filter (weight == 1) %>% select(source,target,weight,directed)


newdata_ = read.csv("Data/Connectivity_6.3.csv") %>% filter (weight == 1) 
```

#Network by Block
```{r}

g1 <- graph_from_data_frame(d=newdata_,directed = FALSE)
l = layout_as_tree(g1,flip.y=TRUE,root= "(A2) Main Lobby L2", circular = TRUE)

#plot(g1,layout=l, Vertex.label = NA)

#Edge Color
E(g1)$color <- 'black'
E(g1)$color[E(g1)$BlockConn != "-"] <- 'orange'
E(g1)$color[E(g1)$Staircase != "-"] <- 'orange'

#Node Color 
a = grep("(A1)|(A2)|(A3)|(A4)|(A5)|(A6)",V(g1)$name)
b = grep("(B1)|(B2)|(B3)|(B4)|(B5)|(B6)",V(g1)$name)
c = grep("(C1)|(C2)|(C3)|(C4)|(C5)|(C6)",V(g1)$name)
d = grep("(D1)|(D2)|(D3)|(D4)|(D5)|(D6)",V(g1)$name)
e = grep("(E1)|(E2)|(E3)|(E4)|(E5)|(E6)",V(g1)$name)
w = grep("(W1)|(W2)|(W3)|(W4)|(W5)|(W6)",V(g1)$name)
entrance = grep("Visitor Car|Drop-Off|Drop|Sheltered" ,V(g1)$name)


V(g1)$color<-"black"
V(g1)[a]$color<-"red"
V(g1)[b]$color<-"mediumpurple3"
V(g1)[c]$color<-"deepskyblue3"
V(g1)[d]$color<-"orange"
V(g1)[e]$color<-"hotpink2"
V(g1)[w]$color<-"olivedrab3"
V(g1)[entrance]$color<-"black"

```


#Calculate Centrality Measures
```{r}

#extract centrality measures     
btw = betweenness(g1, v = V(g1), directed = FALSE, weights = NULL,
  nobigint = TRUE, normalized = TRUE)
cls = closeness(g1, v = V(g1), weights = NULL, normalized = TRUE)
deg = degree(g1)
eig = evcent(g1)$vector

#create dataframe
btw_df = as.data.frame(btw)
cls_df = as.data.frame(cls)
deg_df = as.data.frame(deg)
eig_df = as.data.frame(eig)

#bind dataframes
cent_df = setNames(cbind(rownames(btw_df), btw_df, cls_df, deg_df, eig_df, row.names = NULL), 
         c("Name", "Betweenness", "Closeness","Degree","Eigenvector"))

```


1) Betweeness - Spaces with greatest potential for Through Movements (Spine)
2) Closeness - Spaces that are Easiest to Reach (Physical Centres)
3) Degree - Local Connectivity (Hallways)
4) Eigenvector - Spaces which are connected to more other Important Spaces (Hierachy of Spaces)

#Plot All Centralities
```{r}
#betweeness
plot.btw = function(){
  nsize.btw <-setNames((cent_df$Betweenness+0.03)*30,cent_df$name)
  plot(g1, layout = layout_with_kk(g1)*0.7, label.cex = 0.5, vertex.size = nsize.btw, vertex.label.color = "darkgrey") + 
    title("Betweenness Centrality", cex.main = 5, line = -5, adj = 0.1)
  legend("bottomright", legend = c("Block A", "Block B", "Block C", "Block D", "Block E", "Block W", "Same Floor Connections", "Stairs and Bridges"), 
       col = c("red", "mediumpurple3", "deepskyblue3", "orange", "hotpink2", "olivedrab3", "black","orange"), 
       lty = c(NA,NA,NA,NA,NA,NA,1,1), 
       pch = c(19,19,19,19,19,19,NA,NA),
       lwd = 2, cex = 3, bty = "n" )
}

#closeness (physical centre)
plot.cls = function(){
  nsize.cls <-setNames( ((cent_df$Closeness)^3)*2000,cent_df$name)
  plot(g1, layout = layout_with_kk(g1)*0.7, label.cex = 0.5, vertex.size = nsize.cls, vertex.label.color = "darkgrey") + 
    title("Closeness Centrality", cex.main = 5, line = -5, adj = 0.1)
  legend("bottomright", legend = c("Block A", "Block B", "Block C", "Block D", "Block E", "Block W", "Same Floor Connections", "Stairs and Bridges"), 
       col = c("red", "mediumpurple3", "deepskyblue3", "orange", "hotpink2", "olivedrab3", "black","orange"), 
       lty = c(NA,NA,NA,NA,NA,NA,1,1), 
       pch = c(19,19,19,19,19,19,NA,NA),
       lwd = 2, cex = 3, bty = "n" )
}

#degree (central corridors)
plot.deg = function(){
  nsize.deg <-setNames(cent_df$Degree/2,cent_df$name)
  plot(g1, layout = layout_with_kk(g1)*0.7, label.cex = 0.5, vertex.size = nsize.deg, vertex.label.color = "darkgrey") + 
    title("Degree Centrality", cex.main = 5, line = -5, adj = 0.1)
  legend("bottomright", legend = c("Block A", "Block B", "Block C", "Block D", "Block E", "Block W", "Same Floor Connections", "Stairs and Bridges"), 
       col = c("red", "mediumpurple3", "deepskyblue3", "orange", "hotpink2", "olivedrab3", "black","orange"), 
       lty = c(NA,NA,NA,NA,NA,NA,1,1), 
       pch = c(19,19,19,19,19,19,NA,NA),
       lwd = 2, cex = 3, bty = "n" )
}

#eigenvector (heirachy of spaces, most prime areas)
plot.eig = function(){
  nsize.eig <-setNames( ((cent_df$Eigenvector)^0.8)*8,cent_df$name)
  plot(g1, layout = layout_with_kk(g1)*0.7, label.cex = 0.5, vertex.size = nsize.eig, vertex.label.color = "darkgrey") + 
    title("Eigenvector Centrality", cex.main = 5, line = -5, adj = 0.1)
  legend("bottomright", legend = c("Block A", "Block B", "Block C", "Block D", "Block E", "Block W", "Same Floor Connections", "Stairs and Bridges"), 
       col = c("red", "mediumpurple3", "deepskyblue3", "orange", "hotpink2", "olivedrab3", "black","orange"), 
       lty = c(NA,NA,NA,NA,NA,NA,1,1), 
       pch = c(19,19,19,19,19,19,NA,NA),
       lwd = 2, cex = 3, bty = "n" )
}

```


#save diagrams (high res)
```{r}
tiff(filename="tiff/FGraph_btw.tiff", width=10, height=10, units="in",
     pointsize=4, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
plot.btw()
dev.off()

tiff(filename="tiff/FGraph_cls.tiff", width=10, height=10, units="in",
     pointsize=4, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
plot.cls()
dev.off()

tiff(filename="tiff/FGraph_deg.tiff", width=10, height=10, units="in",
     pointsize=4, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
plot.deg()
dev.off()

tiff(filename="tiff/FGraph_eig.tiff", width=10, height=10, units="in",
     pointsize=4, compression="lzw", bg="white", res=600,
     restoreConsole=TRUE)
plot.eig()
dev.off()
```

#save diagrams (png lower res)
```{r}
png(filename="png/FGraph_btw.png", width=3000, height=3000, bg="white", res=300, pointsize=4)
plot.btw()
dev.off()

png(filename="png/FGraph_cls.png", width=3000, height=3000, bg="white", res=300, pointsize=4)
plot.cls()
dev.off()

png(filename="png/FGraph_deg.png", width=3000, height=3000, bg="white", res=300, pointsize=4)
plot.deg()
dev.off()

png(filename="png/FGraph_eig.png", width=3000, height=3000, bg="white", res=300, pointsize=4)
plot.eig()
dev.off()
```
